---
title: "Modelling bank default with FFTrees!"
author: "NickD - email: nickydyakov@gmail.com"
output: html_document
date: "2022-11-19"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.width = 10, fig.asp = 0.618, message = F, warning = F, echo = F)
```

# 1.Loading the needed packages
```{r echo=TRUE}
library(tidyverse)
library(tidymodels)
library(themis)
library(FFTrees)
library(janitor)
```

# 2.Loading the dataset
```{r echo=TRUE}
bank_default <- read_csv("~/Desktop/R/csv/bank_default.csv", col_types = "dfddf") %>%
  clean_names() %>%
  mutate(
    defaulted = fct_recode(defaulted, "TRUE" = "1", "FALSE" = "0"),
    employed = fct_recode(employed, "Yes" = "1", "No" = "0")
  ) %>% select(-index)
```

# 3.EDA
## Checking for missing values
```{r echo=FALSE}
bank_default %>% map_dfr(~ sum(is.na(.)))
```

## Is the target variable ballanced?
```{r}
bank_default %>% 
	count(defaulted) %>% 
	ggplot(aes(n, defaulted, fill = defaulted)) +
	geom_col(show.legend = F)
```

# 4.Splitting the data
```{r echo=TRUE}
set.seed(2022)
split <- initial_split(bank_default, strata = defaulted)
train <- training(split)
test <- testing(split)
val <- slice_sample(bank_default, n = 10)
```

# 5.Building a recipe to ballance the target variable
```{r}
bank_recipe <- recipe(~., train) %>%
  step_downsample(defaulted, under_ratio = 1) %>%
  prep() %>%
  bake(new_data = NULL)
bank_recipe
```

## Is the target variable ballanced now?
```{r}
bank_recipe %>% 
	count(defaulted) %>% 
	ggplot(aes(n, defaulted, fill = defaulted)) +
	geom_col(show.legend = F)
```

```{r}
train_last <- train %>% mutate(defaulted = as.logical(defaulted))
test_last <- test %>% mutate(defaulted = as.logical(defaulted))
```

# 6.Modelling
```{r}
default_fit <- FFTrees(
  formula = defaulted ~ .,
  data = train_last,
  data.test = test_last,
  decision.labels = c("No Default", "Default"),
  do.comp = T
)
default_fit
```

# 7.Plotting the results
```{r fig 04, echo=FALSE}
plot(default_fit,
  data = "test",
  main = "Risk of Default"
)
```

# 8. Predicting on new data
```{r}
predict(default_fit, newdata = val)
```

# 8.Ranking the predictor accuracies
```{r fig 05, echo=FALSE}
plot(default_fit, what = "cues", data = "train")
```

# 9.Comparing predictive performance across algorithms
```{r}
default_fit$competition$test %>%
  mutate_if(is.numeric, round, 3) %>%
  knitr::kable()
```
