---
title: "EDA of UK crimes from 2010 to 2014!"
author: "NickD - email: nickydyakov@gmail.com"
date: "2022-09-03"
output: html_document
---

```{r message = FALSE, warning = FALSE}
# Loading required packages
library(tidyverse)
```

```{r message = FALSE, warning = FALSE}
# Loading the data set
crimes<-read_csv("crimes_uk.csv")
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.width = 10, fig.asp = 0.618, out.width = "100%")
```

## EDA
## Top 10 administrative units with highest number of crimes
```{r fig01, echo = FALSE, message = FALSE, warning = FALSE}
crimes %>% 
  count(cja) %>% 
  mutate(cja = fct_reorder(cja, n)) %>% 
  slice_max(cja, n = 10) %>% 
  ggplot(aes(cja, n, fill = cja)) +
  geom_col() +
  scale_fill_brewer(palette = "Paired") +
  geom_text(aes(label = n), position = position_stack(vjust = 0.5), size = 5) +
  theme(text = element_text(size = 18), legend.position = "none") +
  labs(y = "Number of crimes", x = NULL) +
  coord_flip()
```

## Crime number by year and administrative unit (top 10 only)
```{r fig02, echo = FALSE, message = FALSE, warning = FALSE}
crimes %>% 
  count(year, cja) %>% 
  mutate(cja = fct_reorder(cja, n)) %>% 
  slice_max(cja, n = 50) %>% 
  ggplot(aes(cja, n, fill = cja)) +
  geom_col() +
  scale_fill_brewer(palette = "Paired") +
  geom_text(aes(label = n), position = position_stack(vjust = 0.5), size = 3.5) +
  theme(text = element_text(size = 14), legend.position = "none") +
  labs(y = "Number of crimes", x = NULL) +
  facet_wrap(~year, ncol = 3) +
  coord_flip()
```

## Crime number by year and type of perpetrator
```{r fig03, echo = FALSE, message = FALSE, warning = FALSE}
crimes %>% 
  count(year, type) %>% 
  mutate(type = fct_reorder(type, n)) %>% 
  ggplot(aes(type, log(n), fill = type)) +
  geom_col() +
  scale_fill_brewer(palette = "Dark2") +
  geom_text(aes(label = n), position = position_stack(vjust = 0.5), size = 3.5) +
  theme(text = element_text(size = 14), legend.position = "none") +
  labs(y = "Number of crimes (log scale)", x = NULL) +
  facet_wrap(~year, ncol = 3) +
  coord_flip()
```

## Crime number by year and sex of perpetrator
```{r fig04, echo = FALSE, message = FALSE, warning = FALSE}
crimes %>% 
  mutate(sex = fct_recode(sex, "Other" = "Other (companies, public bodies, etc)")) %>% 
  count(year, sex) %>% 
  mutate(sex = fct_reorder(sex, n)) %>% 
  ggplot(aes(sex, log(n), fill = sex)) +
  geom_col() +
  scale_fill_brewer(palette = "Dark2") +
  geom_text(aes(label = n), position = position_stack(vjust = 0.5), size = 3.5) +
  theme(text = element_text(size = 14), legend.position = "none") +
  labs(y = "Number of crimes (log scale)", x = NULL) +
  facet_wrap(~year, ncol = 3) +
  coord_flip()
```

## Crime number by year and age band
```{r fig05, echo = FALSE, message = FALSE, warning = FALSE}
crimes %>% 
  drop_na(ageband) %>% 
  count(year, ageband) %>% 
  mutate(ageband = fct_reorder(ageband, n)) %>% 
  ggplot(aes(ageband, log(n), fill = ageband)) +
  geom_col() +
  scale_fill_brewer(palette = "Dark2") +
  geom_text(aes(label = n), position = position_stack(vjust = 0.5), size = 3.5) +
  theme(text = element_text(size = 14), legend.position = "none") +
  labs(y = "Number of crimes (log scale)", x = NULL) +
  facet_wrap(~year, ncol = 3) +
  coord_flip()
```

## Crime number by year and age group
```{r fig06, echo = FALSE, message = FALSE, warning = FALSE}
crimes %>% 
  drop_na(agegroup) %>% 
  count(year, agegroup) %>% 
  mutate(agegroup = fct_relevel(agegroup, "10-11", "12-14", "15-17", "18-20", "21-24", "25-29", "30-39",
                                "40-49", "50-59", "60+")) %>% 
  ggplot(aes(agegroup, n, fill = agegroup)) +
  geom_col() +
  scale_fill_brewer(palette = "Paired") +
  geom_text(aes(label = n), position = position_stack(vjust = 0.5), size = 3.5) +
  theme(text = element_text(size = 14), legend.position = "none") +
  labs(y = "Number of crimes", x = NULL) +
  facet_wrap(~year, ncol = 3) +
  coord_flip()
```

## Case number by year and court type
```{r fig07, echo = FALSE, message = FALSE, warning = FALSE}
crimes %>% 
  drop_na(courttype) %>% 
  count(year, courttype) %>% 
  mutate(courttype = fct_reorder(courttype, n)) %>% 
  ggplot(aes(courttype, n, fill = courttype)) +
  geom_col() +
  scale_fill_brewer(palette = "Dark2") +
  geom_text(aes(label = n), position = position_stack(vjust = 0.5), size = 3.5) +
  theme(text = element_text(size = 14), legend.position = "none") +
  labs(y = "Number of cases", x = NULL) +
  facet_wrap(~year, ncol = 3) +
  coord_flip()
```

## Crime number by year and offence type
```{r fig08, echo = FALSE, message = FALSE, warning = FALSE}
crimes %>% 
  drop_na(offencetype) %>% 
  count(year, offencetype) %>% 
  mutate(offencetype = fct_reorder(offencetype, n)) %>% 
  ggplot(aes(offencetype, n, fill = offencetype)) +
  geom_col() +
  scale_fill_brewer(palette = "Dark2") +
  geom_text(aes(label = n), position = position_stack(vjust = 0.5), size = 3.5) +
  theme(text = element_text(size = 14), legend.position = "none") +
  labs(y = "Number of crimes", x = NULL) +
  facet_wrap(~year, ncol = 3) +
  coord_flip()
```

## Crime number by year and offence group
```{r fig09, echo = FALSE, message = FALSE, warning = FALSE}
crimes %>% 
  drop_na(offencegroup) %>% 
  count(year, offencegroup) %>% 
  mutate(offencegroup = fct_reorder(offencegroup, n)) %>% 
  ggplot(aes(offencegroup, n, fill = offencegroup)) +
  geom_col() +
  scale_fill_brewer(palette = "Paired") +
  geom_text(aes(label = n), position = position_stack(vjust = 0.5), size = 3.5) +
  theme(text = element_text(size = 14), legend.position = "none") +
  labs(y = "Number of crimes", x = NULL) +
  facet_wrap(~year, ncol = 3) +
  coord_flip()
```

## Crime number by year and offence (top 10 only)
```{r fig10, echo = FALSE, message = FALSE, warning = FALSE}
crimes %>% 
  drop_na(offence) %>% 
  count(year, offence) %>% 
  mutate(offence = fct_reorder(offence, n)) %>% 
  slice_max(offence, n = 50) %>% 
  ggplot(aes(offence, n, fill = offence)) +
  geom_col() +
  scale_fill_brewer(palette = "Paired") +
  geom_text(aes(label = n), position = position_stack(vjust = 0.5), size = 3.5) +
  theme(text = element_text(size = 14), legend.position = "none", 
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(y = NULL, x = NULL) +
  facet_wrap(~year, ncol = 3) +
  coord_flip()
```

## Number of cases by year and verdict
```{r fig11, echo = FALSE, message = FALSE, warning = FALSE}
crimes %>% 
  drop_na(found_guilty) %>% 
  count(year, found_guilty) %>% 
  mutate(found_guilty = fct_reorder(found_guilty, n)) %>% 
  ggplot(aes(found_guilty, n, fill = found_guilty)) +
  geom_col() +
  scale_fill_brewer(palette = "Dark2") +
  geom_text(aes(label = n), position = position_stack(vjust = 0.5), size = 3.5) +
  theme(text = element_text(size = 14), legend.position = "none") +
  labs(y = "Number of cases", x = NULL) +
  facet_wrap(~year, ncol = 3) +
  coord_flip()
```

## Number of cases by year and sentence
```{r fig12, echo = FALSE, message = FALSE, warning = FALSE}
crimes %>% 
  drop_na(sentenced) %>% 
  count(year, sentenced) %>% 
  mutate(sentenced = fct_reorder(sentenced, n)) %>% 
  ggplot(aes(sentenced, n, fill = sentenced)) +
  geom_col() +
  scale_fill_brewer(palette = "Dark2") +
  geom_text(aes(label = n), position = position_stack(vjust = 0.5), size = 3.5) +
  theme(text = element_text(size = 14), legend.position = "none") +
  labs(y = "Number of cases", x = NULL) +
  facet_wrap(~year, ncol = 3) +
  coord_flip()
```

## Number of cases by year and detailed sentence (top 10 only)
```{r fig13, echo = FALSE, message = FALSE, warning = FALSE}
crimes %>% 
  drop_na(detailed_sentence) %>% 
  filter(!detailed_sentence == "Other") %>% 
  count(year, detailed_sentence) %>% 
  mutate(detailed_sentence = fct_reorder(detailed_sentence, n)) %>% 
  slice_max(detailed_sentence, n = 50) %>% 
  ggplot(aes(detailed_sentence, log(n), fill = detailed_sentence)) +
  geom_col() +
  scale_fill_brewer(palette = "Paired") +
  geom_text(aes(label = n), position = position_stack(vjust = 0.5), size = 3.5) +
  theme(text = element_text(size = 14), legend.position = "none") +
  labs(y = "Number of cases (log scale)", x = NULL) +
  facet_wrap(~year, ncol = 3) +
  coord_flip()
```

## Number of cases by year and sentence length (top 10 only)
```{r fig14, echo = FALSE, message = FALSE, warning = FALSE}
crimes %>% 
  drop_na(sentencelength) %>% 
  count(year, sentencelength) %>% 
  mutate(sentencelength = fct_reorder(sentencelength, n)) %>% 
  slice_max(sentencelength, n = 50) %>% 
  ggplot(aes(sentencelength, n, fill = sentencelength)) +
  geom_col() +
  scale_fill_brewer(palette = "Paired") +
  geom_text(aes(label = n), position = position_stack(vjust = 0.5), size = 3.5) +
  theme(text = element_text(size = 14), legend.position = "none") +
  labs(y = "Number of cases", x = NULL) +
  facet_wrap(~year, ncol = 3) +
  coord_flip()
```