---
title: "Sentiment analysis of Tailor Swift's song lyrics!"
author: "NickD - email: nickydyakov@gmail.com"
date: "2022-09-10"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.width = 10, fig.asp = 0.618, message = F, warning = F, echo = F)
```

## 1.Loading needed packages
```{r echo=TRUE}
library(tidyverse)
library(tidytext)
library(patchwork)
library(wordcloud)
library(reshape2)
```

## 2.Loading the dataset
```{r echo=TRUE}
taylor_swift <- read_csv("~/Desktop/R/csv/taylorswift.csv", col_types = "fffffDc") %>% 
  janitor::clean_names() %>% 
  select(-1)
```

```{r}
# Tidying
tidy_taylor_swift<-taylor_swift %>% 
  unnest_tokens(word, lyric)
```

```{r}
# Loading the NRC lexicon for positive and negative sentiments
nrc_positive <- get_sentiments("nrc") %>%
  filter(sentiment == "positive")
nrc_negative <- get_sentiments("nrc") %>%
  filter(sentiment == "negative")
```

## 3.Fearless (2008)
```{r}
# Loading the stop-words data set and joining with Amazon data
fearless<-tidy_taylor_swift %>% 
  filter(album == "Fearless")
data(stop_words)
df_fearless <- fearless %>%
  anti_join(stop_words, by = "word")
```

```{r fig 01}
# Most popular positive words
p1<-df_fearless %>%
  inner_join(nrc_positive, by = "word") %>%
  count(word, sort = TRUE) %>% 
  filter(n > 5) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill = "#00BFC4") +
  labs(title = "Positive words", x = NULL) +
  theme(text = element_text(size = 16)) +
  coord_flip()

# Most popular negative words
p2<-df_fearless %>%
  inner_join(nrc_negative, by = "word") %>%
  count(word, sort = TRUE) %>% 
  filter(n > 3) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill = "#F8766D") +
  labs(title = "Negative words", x = NULL) +
  theme(text = element_text(size = 16)) +
  coord_flip()
p1 + p2
```

## 3.1 Wordcloud
```{r fig 02}
pal<-brewer.pal(8, "Dark2")
df_fearless %>%
anti_join(stop_words, by = "word") %>%
count(word) %>%
with(wordcloud(word, n, max.words = 100, colors = pal, random.color = T))
```

## 3.2 Positive and negative wordcloud
```{r fig 03}
df_fearless %>%
inner_join(get_sentiments("bing"), by = "word") %>%
count(word, sentiment, sort = TRUE) %>%
acast(word ~ sentiment, value.var = "n", fill = 0) %>%
comparison.cloud(colors = c("#F8766D", "#00BFC4"), max.words = 100)
```

## 4.1989 (2014)
```{r}
# Loading the stop-words data set and joining with Amazon data
ts_1989<-tidy_taylor_swift %>% 
  filter(album == "1989")
data(stop_words)
ts_1989 <- ts_1989 %>%
  anti_join(stop_words, by = "word")
```

```{r fig 04}
# Most popular positive words
p3<-ts_1989 %>%
  inner_join(nrc_positive, by = "word") %>%
  count(word, sort = TRUE) %>% 
  filter(n > 3) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill = "#00BFC4") +
  labs(title = "Positive words", x = NULL) +
  theme(text = element_text(size = 16)) +
  coord_flip()

# Most popular negative words
p4<-ts_1989 %>%
  inner_join(nrc_negative, by = "word") %>%
  count(word, sort = TRUE) %>% 
  filter(n > 3) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill = "#F8766D") +
  labs(title = "Negative words", x = NULL) +
  theme(text = element_text(size = 16)) +
  coord_flip()
p3 + p4
```

## 4.1 Wordcloud
```{r fig 05}
pal<-brewer.pal(8, "Dark2")
ts_1989 %>%
anti_join(stop_words, by = "word") %>%
count(word) %>%
with(wordcloud(word, n, max.words = 100, colors = pal, random.color = T))
```

## 4.2 Positive and negative wordcloud
```{r fig 06}
ts_1989 %>%
inner_join(get_sentiments("bing"), by = "word") %>%
count(word, sentiment, sort = TRUE) %>%
acast(word ~ sentiment, value.var = "n", fill = 0) %>%
comparison.cloud(colors = c("#F8766D", "#00BFC4"), max.words = 100)
```

## 5.Red (2012)
```{r}
# Loading the stop-words data set and joining with Amazon data
red<-tidy_taylor_swift %>% 
  filter(album == "Red (Deluxe Edition)")
data(stop_words)
df_red <- red %>%
  anti_join(stop_words, by = "word")
```

```{r fig 07}
# Most popular positive words
p5<-df_red %>%
  inner_join(nrc_positive, by = "word") %>%
  count(word, sort = TRUE) %>% 
  filter(n > 3) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill = "#00BFC4") +
  labs(title = "Positive words", x = NULL) +
  theme(text = element_text(size = 16)) +
  coord_flip()

# Most popular negative words
p6<-df_red %>%
  inner_join(nrc_negative, by = "word") %>%
  count(word, sort = TRUE) %>% 
  filter(n > 3) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill = "#F8766D") +
  labs(title = "Negative words", x = NULL) +
  theme(text = element_text(size = 16)) +
  coord_flip()
p5 + p6
```

## 5.1 Wordcloud
```{r fig 08}
pal<-brewer.pal(8, "Dark2")
df_red %>%
anti_join(stop_words, by = "word") %>%
count(word) %>%
with(wordcloud(word, n, max.words = 100, colors = pal, random.color = T))
```

## 5.2 Positive and negative wordcloud
```{r fig 09}
df_red %>%
inner_join(get_sentiments("bing"), by = "word") %>%
count(word, sentiment, sort = TRUE) %>%
acast(word ~ sentiment, value.var = "n", fill = 0) %>%
comparison.cloud(colors = c("#F8766D", "#00BFC4"), max.words = 100)
```

## 6.Taylor Swift (2006)
```{r}
# Loading the stop-words data set and joining with Amazon data
ts<-tidy_taylor_swift %>% 
  filter(album == "Taylor Swift") %>% 
  mutate(word = str_remove_all(word, "[:number:]"))
data(stop_words)
df_ts <- ts %>%
  anti_join(stop_words, by = "word")
```

```{r fig 10}
# Most popular positive words
p7<-df_ts %>%
  inner_join(nrc_positive, by = "word") %>%
  count(word, sort = TRUE) %>% 
  filter(n > 5) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill = "#00BFC4") +
  labs(title = "Positive words", x = NULL) +
  theme(text = element_text(size = 16)) +
  coord_flip()

# Most popular negative words
p8<-df_ts %>%
  inner_join(nrc_negative, by = "word") %>%
  count(word, sort = TRUE) %>% 
  filter(n > 3) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill = "#F8766D") +
  labs(title = "Negative words", x = NULL) +
  theme(text = element_text(size = 16)) +
  coord_flip()
p7 + p8
```

## 6.1 Wordcloud
```{r fig 11}
pal<-brewer.pal(8, "Dark2")
df_ts %>%
anti_join(stop_words, by = "word") %>%
count(word) %>%
with(wordcloud(word, n, max.words = 100, colors = pal, random.color = T))
```

## 6.2 Positive and negative wordcloud
```{r fig 12}
df_ts %>%
inner_join(get_sentiments("bing"), by = "word") %>%
count(word, sentiment, sort = TRUE) %>%
acast(word ~ sentiment, value.var = "n", fill = 0) %>%
comparison.cloud(colors = c("#F8766D", "#00BFC4"), max.words = 100)
```

## 7.Speak Now (2010)
```{r}
# Loading the stop-words data set and joining with Amazon data
speak_now<-tidy_taylor_swift %>% 
  filter(album == "Speak Now")
data(stop_words)
df_speak_now <- speak_now %>%
  anti_join(stop_words, by = "word")
```

```{r fig 13}
# Most popular positive words
p9<-df_speak_now %>%
  inner_join(nrc_positive, by = "word") %>%
  count(word, sort = TRUE) %>% 
  filter(n > 5) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill = "#00BFC4") +
  labs(title = "Positive words", x = NULL) +
  theme(text = element_text(size = 16)) +
  coord_flip()

# Most popular negative words
p10<-df_speak_now %>%
  inner_join(nrc_negative, by = "word") %>%
  count(word, sort = TRUE) %>% 
  filter(n > 3) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill = "#F8766D") +
  labs(title = "Negative words", x = NULL) +
  theme(text = element_text(size = 16)) +
  coord_flip()
p9 + p10
```

## 7.1 Wordcloud
```{r fig 14}
pal<-brewer.pal(8, "Dark2")
df_speak_now %>%
anti_join(stop_words, by = "word") %>%
count(word) %>%
with(wordcloud(word, n, max.words = 100, colors = pal, random.color = T))
```

## 7.2 Positive and negative wordcloud
```{r fig 15}
df_speak_now %>%
inner_join(get_sentiments("bing"), by = "word") %>%
count(word, sentiment, sort = TRUE) %>%
acast(word ~ sentiment, value.var = "n", fill = 0) %>%
comparison.cloud(colors = c("#F8766D", "#00BFC4"), max.words = 100)
```

## 8.Reputation (2017)
```{r}
# Loading the stop-words data set and joining with Amazon data
reputation<-tidy_taylor_swift %>% 
  filter(album == "reputation")
data(stop_words)
df_reputation <- reputation %>%
  anti_join(stop_words, by = "word")
```

```{r fig 16}
# Most popular positive words
p11<-df_reputation %>%
  inner_join(nrc_positive, by = "word") %>%
  count(word, sort = TRUE) %>% 
  filter(n > 5) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill = "#00BFC4") +
  labs(title = "Positive words", x = NULL) +
  theme(text = element_text(size = 16)) +
  coord_flip()

# Most popular negative words
p12<-df_reputation %>%
  inner_join(nrc_negative, by = "word") %>%
  count(word, sort = TRUE) %>% 
  filter(n > 3) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill = "#F8766D") +
  labs(title = "Negative words", x = NULL) +
  theme(text = element_text(size = 16)) +
  coord_flip()
p11 + p12
```

## 8.1 Wordcloud
```{r fig 17}
pal<-brewer.pal(8, "Dark2")
df_reputation %>%
anti_join(stop_words, by = "word") %>%
count(word) %>%
with(wordcloud(word, n, max.words = 100, colors = pal, random.color = T))
```

## 8.2 Positive and negative wordcloud
```{r fig 18}
df_reputation %>%
inner_join(get_sentiments("bing"), by = "word") %>%
count(word, sentiment, sort = TRUE) %>%
acast(word ~ sentiment, value.var = "n", fill = 0) %>%
comparison.cloud(colors = c("#F8766D", "#00BFC4"), max.words = 100)
```

## 9.Folklore (2020)
```{r}
# Loading the stop-words data set and joining with Amazon data
folklore<-tidy_taylor_swift %>% 
  filter(album == "folklore")
data(stop_words)
df_folklore <- folklore %>%
  anti_join(stop_words, by = "word")
```

```{r fig 19}
# Most popular positive words
p13<-df_folklore %>%
  inner_join(nrc_positive, by = "word") %>%
  count(word, sort = TRUE) %>% 
  filter(n > 3) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill = "#00BFC4") +
  labs(title = "Positive words", x = NULL) +
  theme(text = element_text(size = 16)) +
  coord_flip()

# Most popular negative words
p14<-df_folklore %>%
  inner_join(nrc_negative, by = "word") %>%
  count(word, sort = TRUE) %>% 
  filter(n > 2) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill = "#F8766D") +
  labs(title = "Negative words", x = NULL) +
  theme(text = element_text(size = 16)) +
  coord_flip()
p13 + p14
```

## 9.1 Wordcloud
```{r fig 20}
pal<-brewer.pal(8, "Dark2")
df_folklore %>%
anti_join(stop_words, by = "word") %>%
count(word) %>%
with(wordcloud(word, n, max.words = 100, colors = pal, random.color = T))
```

## 9.2 Positive and negative wordcloud
```{r fig 21}
df_folklore %>%
inner_join(get_sentiments("bing"), by = "word") %>%
count(word, sentiment, sort = TRUE) %>%
acast(word ~ sentiment, value.var = "n", fill = 0) %>%
comparison.cloud(colors = c("#F8766D", "#00BFC4"), max.words = 100)
```