---
title: "Exploratory data analysis, inferential statistics, modeling, and visualizations!"
output: html_document
date: "2022-11-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 6, fig.asp = 0.618, message = F, warning = F, echo = F, out.width = 800)
```

# 1.Libraries
```{r echo=TRUE}
library(tidyverse)
library(readxl)
library(ggstatsplot)
library(DataExplorer)
library(dlookr)
library(flextable)
library(DT)
library(jmv)
library(pwr)
library(eurostat)
library(rnaturalearth)
library(rnaturalearthdata)
library(leaflet)
library(factoextra)
library(FactoMineR)
library(ggpubr)
```

# 2.Datasets
```{r echo=TRUE}
diss <- read_csv("~/Desktop/R/data/diss.csv") %>% mutate_if(is.character, as.factor)
t_test <- read_excel("~/Desktop/R/various/jam_data.xlsx", sheet = 14)
one_way_anova <- read_excel("~/Desktop/R/various/jam_data.xlsx", sheet = 20)
sheet_15 <- read_excel("~/Desktop/R/various/jam_data.xlsx", sheet = 15)
sheet_25 <- read_excel("~/Desktop/R/various/jam_data.xlsx", sheet = 25)
sheet_1 <- read_excel("~/Desktop/R/various/jam_data.xlsx", sheet = 1)
sheet_18 <- read_excel("~/Desktop/R/various/jam_data.xlsx", sheet = 18)
sheet_24 <- read_excel("~/Desktop/R/various/jam_data.xlsx", sheet = 24)
sheet_16 <- read_excel("~/Desktop/R/various/jam_data.xlsx", sheet = 16)
sheet_12 <- read_excel("~/Desktop/R/various/jam_data.xlsx", sheet = 12)
stress <- read_csv("~/Desktop/R/data/stress.csv")
```

# 3.Exploratory data analysis (EDA)
## 3.1.Introductory view of the dataset
```{r}
diss %>% plot_intro(theme_config = list(text = element_text(size = 18)))
```

## 3.2.Comlete overview of selected variables (do not apply for extensive datasets!)
```{r}
diss %>%
  select(1:10) %>%
  flextable()
```

## 3.3.Comlete overview of selected variables with an interactive table
```{r}
diss %>%
  select(1:10) %>%
  datatable()
```

## 3.4.Overview of some statistics of numerical variables only
```{r}
diss %>%
  diagnose_numeric() %>%
  flextable()
```

## 3.5.Descriptive statistics of selected numerical variables
```{r}
diss %>%
  descriptives(
    vars = c(elev, slope, s_ha, s_m2, invasive, rare),
    splitBy = NULL, freq = FALSE,
    desc = "columns", hist = FALSE, dens = FALSE, bar = FALSE,
    barCounts = FALSE, box = F, violin = FALSE, dot = FALSE,
    dotType = "jitter", boxMean = FALSE, boxLabelOutliers = TRUE,
    qq = FALSE, n = TRUE, missing = TRUE, mean = TRUE,
    median = TRUE, mode = F, sum = FALSE, sd = TRUE,
    variance = T, range = T, min = TRUE, max = TRUE,
    se = T, ci = T, ciWidth = 95, iqr = FALSE,
    skew = FALSE, kurt = FALSE, sw = T, pcEqGr = FALSE,
    pcNEqGr = 4, pc = FALSE, pcValues = "25,50,75"
  )
```

## 3.6.Checking for missing values in selected variables or the whole dataset
```{r}
diss %>%
  select(starts_with("x"), total_stems) %>%
  map_dfr(~ sum(is.na(.))) %>%
  flextable()
```

## 3.7.Checking the distribution of numerical variables
```{r}
diss %>% plot_histogram(theme_config = list(text = element_text(size = 18)))
```

## 3.8.Checking for correlation of some of the numerical variables
```{r}
diss %>%
  select(elev, slope, s_ha, s_m2, invasive, rare, tree_cover, herb_cover, shrub_cover) %>%
  plot_correlate()
```

## 3.9.Taking a look at the categorical variables
```{r}
diss %>% plot_bar_category(top = 10, -plot)
```

## 3.10.Taking a look at the categorical variables in the context of a selected categorical variable
```{r}
diss %>% plot_bar(by = "veg_type", binary_as_factor = F, theme_config = list(text = element_text(size = 18)))
```

## 3.11.Plotting numerical variables in the context of a grouping (categorical) variables
```{r}
diss %>%
  select(veg_type, elev, slope, s_ha, s_m2) %>%
  plot_boxplot(by = "veg_type", theme_config = list(text = element_text(size = 18)))
```

# 4.Inferential statistics
## 4.1.Comparing independent samples:
### 4.1.1.Parametric (2 groups) - Student’s and Welch’s t-test
### Assumptions of the test:
- Normality;
- Independence;
- Homogeneity of variance (homoscedasticity).
```{r include=FALSE}
t_test %>% descriptives(splitBy = "tutor", sw = T)
```

```{r}
t_test %>%
  ggbetweenstats(tutor, grade,
    plot.type = "box", type = "p", bf.message = FALSE, xlab = "Tutor",
    ylab = "Grade", centrality.type = "p", centrality.point.args = list(size = 4, color = "darkred"),
    ggplot.component = theme(text = element_text(size = 18), plot.subtitle = element_text(size = 18)),
    centrality.label.args = list(size = 5, nudge_x = 0.4, segment.linetype = 4, min.segment.length = 0)
  )
```

### 4.1.2.Parametric (> 2 groups) - Fisher’s and Welch’s one-way ANOVA
### Assumptions of the test:
- Normality;
- Independence;
```{r include=FALSE}
one_way_anova %>% descriptives(splitBy = "test", sw = T)
```

```{r}
one_way_anova %>%
  ggbetweenstats(test, score,
    plot.type = "box", type = "p", bf.message = FALSE, xlab = "Test",
    ylab = "Score", centrality.type = "p", centrality.point.args = list(size = 4, color = "darkred"),
    ggplot.component = theme(text = element_text(size = 18), plot.subtitle = element_text(size = 18)),
    centrality.label.args = list(size = 5, nudge_x = 0.4, segment.linetype = 4, min.segment.length = 0)
  )
```

### 4.1.3.Nonparametric (2 groups) - Wilcoxon W (Mann-Whitney U) test
```{r}
sheet_15 %>%
  ggbetweenstats(group, scores,
    plot.type = "box", type = "np", bf.message = FALSE, xlab = "Group",
    ylab = "Scores", centrality.type = "np", centrality.point.args = list(size = 4, color = "darkred"),
    ggplot.component = theme(text = element_text(size = 18), plot.subtitle = element_text(size = 18)),
    centrality.label.args = list(size = 5, nudge_x = 0.4, segment.linetype = 4, min.segment.length = 0)
  )
```

### 4.1.4.Nonparametric (> 2 groups) - Kruskal-Wallis Rank Sum Test
```{r}
sheet_25 %>%
  ggbetweenstats(drug, mood.gain,
    plot.type = "box", type = "np", bf.message = FALSE, xlab = "Drug", pairwise.comparisons = F,
    ylab = "Mood gain", centrality.type = "np", centrality.point.args = list(size = 4, color = "darkred"),
    ggplot.component = theme(text = element_text(size = 18), plot.subtitle = element_text(size = 18)),
    centrality.label.args = list(size = 5, nudge_x = 0.4, segment.linetype = 4, min.segment.length = 0)
  )
```

### 4.1.5.Robust (2 groups) - Yuen’s test for trimmed means
```{r}
sheet_15 %>%
  ggbetweenstats(group, scores,
    plot.type = "box", type = "r", bf.message = FALSE, xlab = "Group", pairwise.comparisons = F,
    ylab = "Scores", centrality.type = "r", centrality.point.args = list(size = 4, color = "darkred"),
    ggplot.component = theme(text = element_text(size = 18), plot.subtitle = element_text(size = 18)),
    centrality.label.args = list(size = 5, nudge_x = 0.4, segment.linetype = 4, min.segment.length = 0)
  )
```

### 4.1.6.Robust (> 2 groups) - Heteroscedastic one-way ANOVA for trimmed means
```{r}
sheet_25 %>%
  ggbetweenstats(drug, mood.gain,
    plot.type = "box", type = "r", bf.message = FALSE, xlab = "Drug", pairwise.comparisons = F,
    ylab = "Mood gain", centrality.type = "r", centrality.point.args = list(size = 4, color = "darkred"),
    ggplot.component = theme(text = element_text(size = 18), plot.subtitle = element_text(size = 18)),
    centrality.label.args = list(size = 5, nudge_x = 0.4, segment.linetype = 4, min.segment.length = 0)
  )
```

## 4.2.Comparing dependent (paired) samples
### 4.2.1.Parametric (2 groups) - Student’s t-test
### Assumptions of the test:
- Normality;
- Independence;
- Homogeneity of variance (homoscedasticity).
```{r include=FALSE}
sheet_1 %>% descriptives(splitBy = "treatment", sw = T)
```

```{r}
sheet_1 %>%
  mutate(treatment = fct_relevel(treatment, "before", "after")) %>%
  ggwithinstats(treatment, measurement,
    plot.type = "box", type = "p", bf.message = FALSE, xlab = "Treatment",
    ylab = "Measurement", centrality.type = "p", centrality.point.args = list(size = 4, color = "darkred"),
    ggplot.component = theme(text = element_text(size = 18), plot.subtitle = element_text(size = 18)),
    centrality.label.args = list(size = 5, nudge_x = 0.4, segment.linetype = 4, min.segment.length = 0)
  )
```

### 4.2.2.Parametric (> 2 groups) - Fisher’s one-way repeated measures ANOVA
### Assumptions of the test:
- Normality;
- Independence;
- Homogeneity of variance (homoscedasticity).
```{r include=FALSE}
sheet_18 %>% descriptives(splitBy = "test", sw = T)
```

```{r}
sheet_18 %>%
  ggwithinstats(test, grade,
    plot.type = "box", type = "p", bf.message = FALSE, xlab = "Test", pairwise.comparisons = F,
    ylab = "Grade", centrality.type = "p", centrality.point.args = list(size = 4, color = "darkred"),
    ggplot.component = theme(text = element_text(size = 18), plot.subtitle = element_text(size = 18)),
    centrality.label.args = list(size = 5, nudge_x = 0.4, segment.linetype = 4, min.segment.length = 0)
  )
```

### 4.2.3.Nonparametric (2 groups) - Wilcoxon signed-rank test
```{r}
sheet_1 %>%
  mutate(treatment = fct_relevel(treatment, "before", "after")) %>%
  ggwithinstats(treatment, measurement,
    plot.type = "box", type = "np", bf.message = FALSE, xlab = "Treatment",
    ylab = "Measurement", centrality.type = "np", centrality.point.args = list(size = 4, color = "darkred"),
    ggplot.component = theme(text = element_text(size = 18), plot.subtitle = element_text(size = 18)),
    centrality.label.args = list(size = 5, nudge_x = 0.4, segment.linetype = 4, min.segment.length = 0)
  )
```

### 4.2.4.Nonparametric (> 2 groups) - Friedman rank sum test
```{r}
sheet_18 %>%
  ggwithinstats(test, grade,
    plot.type = "box", type = "np", bf.message = FALSE, xlab = "Test", pairwise.comparisons = F,
    ylab = "Grade", centrality.type = "np", centrality.point.args = list(size = 4, color = "darkred"),
    ggplot.component = theme(text = element_text(size = 18), plot.subtitle = element_text(size = 18)),
    centrality.label.args = list(size = 5, nudge_x = 0.4, segment.linetype = 4, min.segment.length = 0)
  )
```

### 4.2.5.Robust (2 groups) - Yuen’s test on trimmed means for dependent samples
```{r}
sheet_1 %>%
  mutate(treatment = fct_relevel(treatment, "before", "after")) %>%
  ggwithinstats(treatment, measurement,
    plot.type = "box", type = "r", bf.message = FALSE, xlab = "Treatment",
    ylab = "Measurement", centrality.type = "r", centrality.point.args = list(size = 4, color = "darkred"),
    ggplot.component = theme(text = element_text(size = 18), plot.subtitle = element_text(size = 18)),
    centrality.label.args = list(size = 5, nudge_x = 0.4, segment.linetype = 4, min.segment.length = 0)
  )
```

### 4.2.6.Robust (> 2 groups) - Heteroscedastic one-way repeated measures ANOVA for trimmed means
```{r}
sheet_18 %>%
  ggwithinstats(test, grade,
    plot.type = "box", type = "r", bf.message = FALSE, xlab = "Test", pairwise.comparisons = F,
    ylab = "Grade", centrality.type = "r", centrality.point.args = list(size = 4, color = "darkred"),
    ggplot.component = theme(text = element_text(size = 18), plot.subtitle = element_text(size = 18)),
    centrality.label.args = list(size = 5, nudge_x = 0.4, segment.linetype = 4, min.segment.length = 0)
  )
```

## 4.3.Correlation
## 4.3.1.Parametric - Pearson’s r
```{r}
diss %>%
  ggcorrmat(
    cor.vars = c(elev, slope, s_ha, s_m2, invasive, rare), type = "p",
    ggcorrplot.args = list(method = "square", outline.color = "black", pch.cex = 14),
    ggplot.component = theme(text = element_text(size = 18), plot.subtitle = element_text(size = 18))
  )
```

## 4.3.2.Nonparametric - Spearman's ρ
```{r}
diss %>%
  ggcorrmat(
    cor.vars = c(elev, slope, tree_cover, herb_cover, total_stems), type = "np",
    ggcorrplot.args = list(method = "square", outline.color = "black", pch.cex = 14),
    ggplot.component = theme(text = element_text(size = 18), plot.subtitle = element_text(size = 18))
  )
```

## 4.3.3.Robust - Percentage bend correlation
```{r}
diss %>%
  ggcorrmat(
    cor.vars = c(invasive, rare, herb_cover, shrub_cover, tree_cover, total_stems), type = "r",
    ggcorrplot.args = list(method = "square", outline.color = "black", pch.cex = 14),
    ggplot.component = theme(text = element_text(size = 18), plot.subtitle = element_text(size = 18))
  )
```

## 4.4.Scatterplots with statistical details
## 4.4.1.Parametric
```{r}
diss %>%
  ggscatterstats(elev, s_ha,
    type = "p", method = "lm", bf.message = FALSE, xlab = "Elevation (m)", ylab = "Species richness (0.1 ha)",
    ggplot.component = theme(text = element_text(size = 16), plot.subtitle = element_text(size = 16))
  )
```

## 4.4.2.Nonparametric
```{r}
diss %>%
  ggscatterstats(slope, s_m2,
    type = "np", method = "lm", bf.message = FALSE, xlab = "Slope (º)", ylab = "Species richness (1 m2)",
    ggplot.component = theme(text = element_text(size = 16), plot.subtitle = element_text(size = 16))
  )
```

## 4.4.3.Robust
```{r}
diss %>%
  ggscatterstats(herb_cover, invasive,
    type = "r", method = "lm", bf.message = FALSE, xlab = "Herb cover (%)", ylab = "Invasive species number (0.1 ha)",
    ggplot.component = theme(text = element_text(size = 16), plot.subtitle = element_text(size = 16))
  )
```

## 4.5.Bar charts for categorical data with statistical details
## 4.5.1.Parametric (unpaired) - Pearson's χ2
### Assumptions of the test:
- Expected frequencies are sufficiently large;
- Data are independent of one another.
```{r}
sheet_24 %>%
  ggbarstats(choice, species,
    bf.message = FALSE,
    legend.title = "Choice:", xlab = "Species", ylab = NULL,
    ggplot.component = theme(text = element_text(size = 18))
  )
```

## 4.5.2.Parametric (paired) - McNemar’s test
```{r}
sheet_16 %>%
  mutate(treatment = fct_relevel(treatment, "before", "after")) %>%
  ggbarstats(response, treatment,
    bf.message = FALSE, paired = T,
    legend.title = "Response:", xlab = "Treatment", ylab = NULL,
    ggplot.component = theme(text = element_text(size = 18))
  )
```

## 4.6.Pie charts for categorical data with statistical details
## 4.6.1.Parametric - One-sample proportion test
```{r}
diss %>%
  ggpiestats(exp,
    bf.message = FALSE,
    legend.title = "Exposition:", xlab = NULL, ylab = NULL,
    ggplot.component = theme(text = element_text(size = 18))
  )
```

## 4.7.Dot-and-whisker plots for regression analyses
```{r}
mod <- lm(invasive ~ elev + slope + s_ha + s_m2, data = diss)
```

```{r}
ggcoefstats(mod,
  bf.message = FALSE, xlab = "Estimate", ylab = "Term",
  title = "What and how influences the distribution of invasive plant species?\nTerm names from top to bottom: \n- species richness/1 m2; \n- species richness/0.1 ha; \n- slope; \n- elevation",
  stats.label.args = list(size = 4, direction = "y", min.segment.length = 0),
  vline.args = list(size = 0.5, linetype = "dashed"), exclude.intercept = T,
  ggplot.component = theme(text = element_text(size = 18))
)
```

## 4.8.Histograms with statistical details from one-sample tests
```{r}
diss %>%
  gghistostats(
    x = s_ha, type = "np", test.value = 45, bf.message = F, centrality.type = "np",
    ggplot.component = theme(text = element_text(size = 16), plot.subtitle = element_text(size = 16)),
    xlab = "Species richness/0.1 ha"
  )
```

## 4.9.Power analysis
```{r}
an <- pwr.anova.test(k = 4, n = NULL, f = 0.25, sig.level = 0.05, power = 0.8)
plot(an, xlab = "Sample size", ylab = "Power")
```

# 5.Modelling
## 5.1.Linear regression
### Assumptions of linear regression:
- Normality;
- Linearity;
- Homogeneity of variance;
- Uncorrelated predictors;
- Residuals are independent of each other;
- No “bad” outliers.
```{r}
sheet_12 %>%
  linReg(
    dep = dan.grump,
    covs = vars(dan.sleep, baby.sleep),
    factors = NULL,
    blocks = list(list("dan.sleep", "baby.sleep")),
    refLevels = NULL,
    intercept = "refLevel",
    r = TRUE,
    r2 = TRUE,
    r2Adj = TRUE,
    aic = TRUE,
    bic = FALSE,
    rmse = TRUE,
    modelTest = TRUE,
    anova = F,
    ci = FALSE,
    ciWidth = 95,
    stdEst = FALSE,
    ciStdEst = FALSE,
    ciWidthStdEst = 95,
    norm = TRUE,
    qqPlot = F,
    resPlots = FALSE,
    durbin = FALSE,
    collin = T,
    cooks = FALSE,
    emMeans = list(list()),
    ciEmm = TRUE,
    ciWidthEmm = 95,
    emmPlots = TRUE,
    emmTables = FALSE,
    emmWeights = TRUE
  )
```

## 5.1.Binomial logistic regression
```{r}
stress %>% 
	logRegBin(
  dep = stress,
  covs = vars(stability, flexibility, tasks, lack_train, lack_car_dev),
  factors = NULL,
  blocks = list(list("stability", "flexibility", "tasks", "lack_train", "lack_car_dev")),
  refLevels = list(list(var = "stress", ref = "Unstressed")),
  modelTest = TRUE,
  dev = TRUE,
  aic = TRUE,
  bic = FALSE,
  pseudoR2 = list("r2mf"),
  omni = FALSE,
  ci = FALSE,
  ciWidth = 95,
  OR = FALSE,
  ciOR = FALSE,
  ciWidthOR = 95,
  emMeans = list(list()),
  ciEmm = FALSE,
  ciWidthEmm = 95,
  emmPlots = FALSE,
  emmTables = FALSE,
  emmWeights = FALSE,
  class = TRUE,
  acc = TRUE,
  spec = TRUE,
  sens = TRUE,
  auc = TRUE,
  rocPlot = TRUE,
  cutOff = 0.5,
  cutOffPlot = FALSE,
  collin = TRUE,
  boxTidwell = FALSE,
  cooks = FALSE
)
```

# 6.Visualizations
## 6.1.Maps
```{r}
eurasia <- 
	ne_countries(
  scale = 50,
  type = "sovereignty",
  continent = c("Europe", "Asia"),
  country = NULL,
  geounit = NULL,
  sovereignty = NULL,
  returnclass = c("sf")) %>%
  select(name, iso_a2, continent, subregion, geometry) %>%
  mutate(
    name = fct_recode(name,
      "Czechia" = "Czech Rep.",
      "North Macedonia" = "Macedonia",
      "Bosnia and Herzegovina" = "Bosnia and Herz."))
ilc_di12 <- get_eurostat("ilc_di12", type = "label", time_format = "date") %>%
  mutate_if(is_character, as_factor) %>%
  mutate(geo = fct_recode(
    geo,
    "Germany" = "Germany (until 1990 former territory of the FRG)",
    "Turkey" = "Türkiye"))
eu <- ilc_di12 %>%
  filter(time == "2007-01-01") %>%
  group_by(geo) %>%
  summarise(sm = sum(values)) %>%
  mutate_if(is.numeric, round, 1)
df <- eurasia %>%
  inner_join(eu, by = c("name" = "geo"))
df %>%
  ggplot() +
  geom_sf(aes(fill = sm), alpha = 0.4) +
  coord_sf(xlim = c(-15, 40), ylim = c(34, 73), expand = FALSE) +
  geom_sf_text(aes(label = sm), size = 3) +
  scale_fill_distiller(palette = "Spectral") +
  labs(
    x = NULL, y = NULL, fill = "Години:",
    title = "Gini, 2021 (0 = max equality, 100 = max inequality)"
  ) +
  theme(text = element_text(size = 16), legend.position = "none")
```

## 6.2.Interactive maps
```{r}
st_karadjovo <- read_csv("~/Desktop/R/data/st_karadjovo.csv")
pal <- colorNumeric("magma", domain = st_karadjovo$alt)
leaflet() %>%
	addTiles() %>%
	addCircles(data = st_karadjovo, color = ~ pal(alt), weight = 4)
```

## 6.3.Cluster analyses
### 6.3.1.K-means clustering
```{r}
df <- load("~/Desktop/R/clustering/clustering.RData")
```

```{r}
df <- scale(env_clust)
res.dist <- get_dist(df, method = "euclidean", stand = FALSE)
km.res <- fviz_nbclust(
  df,
  FUNcluster = kmeans,
  method = "wss",
  diss = NULL,
  k.max = 10,
  nboot = 100,
  verbose = TRUE,
  barfill = "steelblue",
  barcolor = "steelblue",
  linecolor = "steelblue",
  print.summary = TRUE,
)
km.res <- kmeans(df, 6, nstart = 50)
fviz_cluster(
  km.res,
  data = df,
  stand = TRUE,
  axes = 1:2,
  geom = c("point"),
  repel = TRUE,
  show.clust.cent = TRUE,
  ellipse = TRUE,
  ellipse.type = "convex",
  ellipse.level = 0.95,
  ellipse.alpha = 0.1,
  shape = NULL,
  pointsize = 1.5,
  labelsize = 16,
  main = "K-means clustering",
  xlab = NULL,
  ylab = NULL,
  outlier.color = "black",
  outlier.shape = 19,
  outlier.pointsize = pointsize,
  outlier.labelsize = labelsize,
  ggtheme = theme_minimal())
```

### 6.3.2.Hierarchical clustering
```{r}
res.hc <- hclust(d = res.dist, method = "ward.D2")
fviz_dend(
  x = res.hc,
  k = 6,
  h = NULL,
  k_colors = "simpsons",
  palette = "simpsons",
  show_labels = TRUE,
  color_labels_by_k = TRUE,
  label_cols = NULL,
  labels_track_height = 1.0,
  repel = FALSE,
  lwd = 0.8,
  type = "rectangle",
  phylo_layout = "layout.auto",
  rect = TRUE,
  rect_border = "gray",
  rect_lty = 2,
  rect_fill = FALSE,
  lower_rect = 0,
  horiz = FALSE,
  cex = 0.7,
  main = "Ward D2 clustering dendrogram",
  xlab = "",
  ylab = "Height",
  sub = NULL,
  ggtheme = theme_classic())
```

## 6.4.Ordination
### 6.4.1.Principal Component Analysis (PCA)
```{r}
diss <- read_csv("~/Desktop/R/data/diss.csv")
data <- diss %>% column_to_rownames(var = "plot") %>% 
  select(elev:annuals)
com_types <- diss %>% as_tibble() %>%
  select(plot, com) %>%
  column_to_rownames(var = "plot")
```

```{r}
res.pca<-PCA(data, scale.unit = TRUE, ncp = 5, ind.sup = NULL,
             quanti.sup = NULL, quali.sup = NULL, row.w = NULL,
             col.w = NULL, graph = F, axes = c(1,2))
```

```{r}
pca_biplot<-fviz_pca_biplot(
  X = res.pca,
  axes = 1:2,
  geom.ind = c("point"),
  geom.var = c("arrow", "text"),
  select.var = list(contrib = 10),
  col.ind = com_types$com,
  fill.ind = com_types$com,
  col.var = "black",
  fill.var = "black",
  gradient.cols = NULL,
  label = "all",
  invisible = "none",
  repel = TRUE,
  habillage = "none",
  palette = "simpsons",
  addEllipses = FALSE,
  ellipse.type = "convex",
  title = NULL,
  pointshape = 21,
  pointsize = 3,
  labelsize = 5,
  arrowsize = 0.7,
  mean.point = FALSE,
  legend.title = "Community types",
  xlab = "PCA1 (37.8%)",
  ylab = "PCA2 (17%)")
```

```{r}
ggpar(
  pca_biplot,
  palette = "simpsons",
  gradient.cols = NULL,
  main = NULL,
  submain = NULL,
  caption = NULL,
  xlab = "PCA1",
  ylab = "PCA2",
  title = NULL,
  subtitle = NULL,
  font.main = 16,
  font.submain = NULL,
  font.x = 16,
  font.y = 16,
  font.caption = NULL,
  font.title = NULL,
  font.subtitle = NULL,
  font.family = "",
  xlim = NULL,
  ylim = NULL,
  xscale = c("none", "log2", "log10", "sqrt"),
  yscale = c("none", "log2", "log10", "sqrt"),
  format.scale = FALSE,
  legend = "right",
  legend.title = "Vegetation\nTypes",
  font.legend = 16,
  ticks = TRUE,
  tickslab = TRUE,
  font.tickslab = 16,
  font.xtickslab = 16,
  font.ytickslab = 16,
  x.text.angle = NULL,
  y.text.angle = NULL,
  xtickslab.rt = NULL,
  ytickslab.rt = NULL,
  xticks.by = NULL,
  yticks.by = NULL,
  rotate = FALSE,
  orientation = c("vertical", "horizontal", "reverse"),
  ggtheme = theme_classic())
```