---
title: "Stroke prediction with FFTrees algorithm!"
author: "NickD - email: nickydyakov@gmail.com"
output: html_document
date: "2022-11-17"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.width = 10, fig.asp = 0.618, message = F, warning = F, echo = F)
```

# 1.Loading the needed packages
```{r echo=TRUE}
library(tidyverse)
library(FFTrees)
library(DT)
```

# 2.Loading the dataset
```{r echo=TRUE}
stroke <- read_csv("~/Desktop/R/csv/stroke.csv", col_types = "dfdfffffddff") %>%
  mutate(
    stroke = fct_recode(stroke, "TRUE" = "1", "FALSE" = "0"),
    hypertension = fct_recode(hypertension, "Yes" = "1", "No" = "0"),
    heart_disease = fct_recode(heart_disease, "Yes" = "1", "No" = "0"),
    stroke = as.logical(stroke)
  ) %>%
  mosaic::shuffle() %>% 
	select(-id, -orig.id)
datatable(stroke)
```

# 3. EDA
## Checking for missing values
```{r echo=FALSE}
stroke %>% map_dfr(~ sum(is.na(.)))
stroke <- stroke %>% drop_na(bmi)
stroke %>% map_dfr(~ sum(is.na(.)))
```

## Plotting the numerical (predictor) variables
```{r fig 01, echo=FALSE}
stroke %>%
  select(where(is.numeric)) %>%
  pivot_longer(1:3, names_to = "name", values_to = "value") %>%
  ggplot(aes(value)) +
  geom_histogram() +
  labs(x = "Value", y = "Count") +
  theme(text = element_text(size = 12)) +
  facet_wrap(~name)
```

## Plotting the nominal (predictor) variables
```{r fig 02, echo=FALSE}
stroke %>%
  count(gender) %>%
  ggplot(aes(n, gender, fill = gender)) +
  geom_col() +
  labs(y = NULL) +
  theme(text = element_text(size = 16))
stroke %>%
  count(hypertension) %>%
  ggplot(aes(n, hypertension, fill = hypertension)) +
  geom_col() +
  labs(y = NULL) +
  theme(text = element_text(size = 16))
stroke %>%
  count(heart_disease) %>%
  ggplot(aes(n, heart_disease, fill = heart_disease)) +
  geom_col() +
  labs(y = NULL) +
  theme(text = element_text(size = 16))
stroke %>%
  count(ever_married) %>%
  ggplot(aes(n, ever_married, fill = ever_married)) +
  geom_col() +
  labs(y = NULL) +
  theme(text = element_text(size = 16))
stroke %>%
  count(work_type) %>%
  ggplot(aes(n, work_type, fill = work_type)) +
  geom_col() +
  labs(y = NULL) +
  theme(text = element_text(size = 16))
stroke %>%
  count(Residence_type) %>%
  ggplot(aes(n, Residence_type, fill = Residence_type)) +
  geom_col() +
  labs(y = NULL) +
  theme(text = element_text(size = 16))
stroke %>%
  count(smoking_status) %>%
  ggplot(aes(n, smoking_status, fill = smoking_status)) +
  geom_col() +
  labs(y = NULL) +
  theme(text = element_text(size = 16))
```

## Plotting the nominal (target) variable
```{r fig 03, echo=FALSE}
stroke %>%
  count(stroke) %>%
  ggplot(aes(n, stroke, fill = stroke)) +
  geom_col() +
  labs(y = NULL) +
  theme(text = element_text(size = 16))
```

# 4.Splitting the data
```{r echo=TRUE}
stroke_train <- stroke %>% slice(1:4000)
stroke_test <- stroke %>% slice(4001:4500)
new_data <- stroke %>% slice(4501:4510)
```

# 5.Modelling
```{r}
stroke_fit <- FFTrees(
  formula = stroke ~ .,
  data = stroke_train,
  data.test = stroke_test,
  decision.labels = c("No Stroke", "Stroke"),
  do.comp = T
)
stroke_fit
```

# 6.Plotting the results
```{r fig 04, echo=FALSE}
plot(stroke_fit,
  data = "test",
  main = "Risk of having a stroke"
)
```

# 7.Ranking the predictor accuracies
```{r fig 05, echo=FALSE}
plot(stroke_fit, what = "cues", data = "train")
```

# 8.Predicting on the new data
```{r echo=FALSE}
predict(stroke_fit, new_data)
```

# 9.Comparing predictive performance across algorithms
```{r}
stroke_fit$competition$test %>% 
	mutate_if(is.numeric, round, 3) %>% 
	datatable()
```